Universal Anonymous Signatures

### 2022-05-10 prism-backend/research/gsac/app-gsac.tex
Updated GSAC and UAS proofs based on updated non-frame definiton.

\begin{proof}[\thmref{thm:correctness-gsac}]
  \todo{XXX}
\end{proof}

\begin{proof}[\thmref{thm:anonymity-gsac}]
  We prove that the probability of an adversary distinguishing signatures by
  challenge users is negligible. For the proof, we restrict to the case of
  allowing only one query to the challenge oracle. The extension to a polynomial
  number of queries given in \cite{bsz05} applies here, with the corresponding
  security loss.

@@

  From $G_1$, we build $G_2$, where within the challenge signature produced by
  \CHALb, we replace the \Ccom value encrypted within \Sign with a random
  string of the appropriate length (e.g., the same length of the encrypted
  message in $G_1$). The corresponding proof for $\NIZKRel_{\Sign}$ is thus
  also simulated. The zero-knowledge and simulation-extractability properties
  of the NIZKs for $\NIZKRel_{\Sign}$, and IND-CCA of the encryption
  scheme, ensure that the result is indistinguishable to the adversary.

@@

\begin{proof}[\thmref{thm:trace-gsac}]
  Assuming the NIZK systems are sound, we build an adversary against existential
  unforgeability of the signature scheme for blocks of committed messages.
  %
  Consider the following events:

  \begin{description}
  \item[$O$.] The \Open algorithm returns $\bot$.
  \item[$J$.] The \Judge algorithm returns $0$.
  \item[$D$.] No credential owned by a user in \CU contains \dattrs.
  \end{description}

@@

  \begin{description}
  \item[$W_1 = O$.] \Open returns $\bot$ (line 5 of \ExpGSACTrace).
  \item[$W_2 = \overline{O} \land J$.] \Open does not fail, but \Judge rejects
    the output of \Open (line 7 of \ExpGSACTrace).
  \item[$W_3 = \overline{O} \land \overline{J} \land D$.] \Open does not fail,
    \Judge accepts the output by \Open, but no corrupt user has a credential
    containing \dattrs (line 8 of \ExpGSACTrace).
  \end{description}

  Clearly, since the group signature is verified at step 4 of the game, if
  verification succeeds, soundness of $\NIZK_{\Sign}$ implies that $(\Ccom_m,
  \Ec,\dattrs) \in \NIZKLang_{\Sign}$, except with negligible probability
  $2^{-\NIZKsecpar}$. Also, observe that each of the winning events for the
  adversary described above are disjoint. Thus:

@@

  $\Pr[W_1]=0$ is directly deduced from the fact that $(\Ccom_m,\Ec,\dattrs)
  \in \NIZKLang_{\Sign}$ due to soundness of $\NIZKRel_{\Sign}$. Concretely,
  we know that \Open does not abort due to rejection of the signature by
  \Verify (as this is checked in line 4 of \ExpGSACTrace too) and, thus,
  $\Ec = \EEnc(\opk,\Ccom)$ which, by correctness of the encryption algorithm,
  implies that $\Ccom = \EDec(\osk,\Ec)$, where $\upk=\Ccom=\CCommit(\usk;0)$.
  Completeness of $\NIZK_{\Open}$ thus implies that the \Open algorithm can
  compute the opening proof \oproof, and return $(\upk,\oproof)$.

@@

  Finally, assume that there is an adversary $\adv$ against \ExpGSACTrace that
  wins by event $W_3$. Then, it is straight forward to build an adversary \advB
  against unforgeability of the signature scheme on blocks of committed
  messages. Namely, \advB creates the parameters with \Setup and the opening
  key pair with \OKeyGen, but instead of running \IKeyGen, sets the verification
  key to the one received in the \ExpSBCMOMF game. In calls by $\adv$ to \OBTISS
  and \ISSUE oracles, \advB replaces the \Issue algorithm with corresponding
  calls to its $\langle \cdot,\SBCMSign \rangle$ oracle. The other oracles are
  unchanged. Without loss of generality, suppose that $\adv$ makes a total of
  $n$ queries to \OBTISS and \ISSUE, combined; which implies that \advB makes
  a total of $n$ queries to its own oracle. If, in such an execution, $\adv$
  wins by event $W_3$, it means that it has produced a signature \sig, revealing
  attribute set \dattrs, that is accepted by \Verify, for which \Open does not
  fail, and for which an honestly generated open proof is accepted by \Judge,
  but such that no issued credential contains \dattrs. Soundness of
  $\NIZK_{\Sign}$ implies that \sig is a valid signature over $\attrs \cup
  \lbrace \usk \rbrace$, and $\dattrs \subseteq \attrs$; but \sig has not been
  produced via a call to the $\langle \cdot,\SBCMSign \rangle$ oracle. Thus,
  \advB can output at least $n+1$ valid signatures, which contradicts security
  of \SBCM.
  %
  By assumption of security of \SBCM, $\Pr[W_3]$ must therefore be negligible in
  $\SBCMsecpar$ and, consequently: $\AdvGSACTrace(\secpar) = \negl(\SBCMsecpar)+
  \negl(\NIZKsecpar)$, which is negligible.  
  \qed
\end{proof}

\begin{proof}[\thmref{thm:frame-gsac}]
  We build an adversary \advB who, given an adversary $\adv$ against
  \ExpGSACNonframe, breaks the hiding property of \C.

@@

  We now build \advB from $G_1$. Recall that \advB is an adversary against
  hiding of \C and, thus, receives a commitment \Ccom, committing to one out
  of two possible messages, $\msg_0$ and $\msg_1$, which \advB picks at random
  from $\AttrSpace$. \advB initializes everything as $G_1$ and, in addition,
  chooses a random integer $u \in [q]$, where $q$ will be the maximim number of
  users to let $\adv$ create via calls to the \HUGEN oracle (note though that
  $q$ can be as large as desired, as it remains a polynomial function of the
  security parameter). In the $u$-th call to the \HUGEN oracle, \advB ignores
  sets $(\upk,\usk)$ to $(\Ccom,\bot)$. Calls to the \OBTAIN and \SIGN oracles
  are dealt with as usual, except when $\adv$ requests credentials or signatures
  on behalf of the $u$-th user. In that cases, \advB simulates the corresponding
  NIZK proofs by calling $\NIZKSim^{\NIZKRel_{\Issue}}$ or
  $\NIZKSim^{\NIZKRel_{\Sign}}$, respectively. Due to the
  simulation-extractability property of both NIZK systems, the output produced
  by the oracles is indistinguishable from that in $G_1$ and, consequently, from
  $G_0=\ExpGSACNonframe$.

  Finally, assume that $\adv$ wins \ExpGSACNonframe with non-negligible
  probability. This means that it outputs a $(\sig = (\Ec,\pi_\sig),\dattrs,
  \msg,\upk,\pi)$, where $(\sig,\dattrs,\msg)$ are accepted by \Verify, and
  $(\upk,\pi,\sig,\dattrs,\msg)$ are accepted by \Judge. Thus, after soundness
  of $\NIZK^{\NIZKRel_{\Sign}}$ and $\NIZK^{\NIZKRel_{\Open}}$, we know that
  \upk is the correct public key associated to an honest user \uid, but as per
  the winning condition, \sig has not been produced via a call to the \SIGN
  oracle for a \cid owned by \uid. Therefore, we can extract the \usk
  corresponding to \upk from the $\pi_{\sig}$ proof. Since executions in the
  environment prepared by \advB are indistinguishable to $\adv$ from executions
  of $G_0$, we can assume that the probability that the \uid associated to the
  \sig output by $\adv$ equals $1/q$. In that case, \usk precisely matches
  $\msg_b$, and \advB wins the hiding game against \C. Since we assume \C
  to be hiding, this probability must therefore be negligible.   
  \qed
\end{proof}

>>>>

\begin{proof}[\thmref{thm:correctness-gsac}; Correctness of \GSACGen]
  \todo{XXX}
\end{proof}

\begin{proof}[\thmref{thm:anonymity-gsac}; Anonymity of \GSACGen]
  We prove that the probability of an adversary distinguishing signatures by
  challenge users is negligible. For the proof, we restrict to the case of
  allowing only one query to the challenge oracle. The extension to a polynomial
  number of queries given in \cite{bsz05} applies here, with the corresponding
  security loss.

@@

  From $G_1$, we build $G_2$, where within the challenge signature produced by
  \CHALb, we replace the values encrypted within \Sign (\Ccom, and all the
  attributes in \attrs) with random strings of the appropriate length (e.g.,
  the same length of their corresponding encrypted messages in $G_1$). The
  proof for $\NIZKRel_{\Sign}$ is thus
  also simulated. The zero-knowledge and simulation-extractability properties
  of the NIZKs for $\NIZKRel_{\Sign}$, and IND-CCA of the encryption
  scheme, ensure that the result is indistinguishable to the adversary.

@@

\begin{proof}[\thmref{thm:trace-gsac}; Traceability of \GSACGen]
  Assuming the NIZK systems are sound, we build an adversary against existential
  unforgeability of the signature scheme for blocks of committed messages.
  %
  Consider the following events:

  \begin{description}
  \item[$O$.] The \Open algorithm returns $\bot$.
  \item[$J$.] The \Judge algorithm returns $0$.
  \item[$D$.] No credential owned by a user in \CU over \attrs contains \dattrs.
  \end{description}

@@

  \begin{description}
  \item[$W_1 = O$.] \Open returns $\bot$ (line 5 of \ExpGSACTrace).
  \item[$W_2 = \overline{O} \land J$.] \Open does not fail, but \Judge rejects
    the output of \Open (line 7 of \ExpGSACTrace).
  \item[$W_3 = \overline{O} \land \overline{J} \land D$.] \Open does not fail,
    \Judge accepts the output by \Open, but no corrupt user has a credential
    over \attrs, containing \dattrs (line 8 of \ExpGSACTrace).
  \end{description}

  Clearly, since the group signature is verified at step 4 of the game, if
  verification succeeds, soundness of $\NIZK_{\Sign}$ implies that $(\Ccom_m,
  \Ec,\sEc^{\attrs},\dattrs,n) \in \NIZKLang_{\Sign}$, except with negligible
  probability $2^{-\NIZKsecpar}$. Also, observe that each of the winning events
  for the adversary described above are disjoint. Thus:

@@

  $\Pr[W_1]=0$ is directly deduced from the fact that $(\Ccom_m,\Ec,
  \sEc^{\attrs},\dattrs,n)
  \in \NIZKLang_{\Sign}$ due to soundness of $\NIZKRel_{\Sign}$. Concretely,
  we know that \Open does not abort due to rejection of the signature by
  \Verify (as this is checked in line 4 of \ExpGSACTrace too) and, thus,
  $\Ec = \EEnc(\opk,\Ccom)$ (resp. $\sEc^{\attrs}_i = \EEnc(\opk,\attrs_i;
  \forall i \in [n]$) which, by correctness of the encryption algorithm,
  implies that $\Ccom = \EDec(\osk,\Ec)$ (resp. $\attrs_i =
  \EDec(\osk,\sEc^{\attrs}_i)$, where $\upk=\Ccom=\CCommit(\usk;0)$.
  Completeness of $\NIZK_{\Open}$ thus implies that the \Open algorithm can
  compute the opening proof \oproof, and return $(\upk,\attrs,\oproof)$.

@@

  Finally, assume that there is an adversary $\adv$ against \ExpGSACTrace that
  wins by event $W_3$. Then, it is straight forward to build an adversary \advB
  against unforgeability of the signature scheme on blocks of committed
  messages. Namely, \advB creates the parameters with \Setup and the opening
  key pair with \OKeyGen, but instead of running \IKeyGen, sets the verification
  key to the one received in the \ExpSBCMOMF game. In calls by $\adv$ to \OBTISS
  and \ISSUE oracles, \advB replaces the \Issue algorithm with corresponding
  calls to its $\langle \cdot,\SBCMSign \rangle$ oracle. The other oracles are
  unchanged. Without loss of generality, suppose that $\adv$ makes a total of
  $n$ queries to \OBTISS and \ISSUE, combined; which implies that \advB makes
  a total of $n$ queries to its own oracle. If, in such an execution, $\adv$
  wins by event $W_3$, it means that it has produced a signature \sig, revealing
  attribute set \dattrs, that is accepted by \Verify, for which \Open does not
  fail, and for which an honestly generated open proof is accepted by \Judge,
  but such that no issued credential over attritube set \attrs that contains
  \dattrs. Soundness of $\NIZK_{\Sign}$ implies that \sig is a valid signature
  over $\attrs \cup \lbrace \usk \rbrace$, and $\dattrs \subseteq \attrs$; but
  \sig has not been produced via a call to the $\langle \cdot,\SBCMSign \rangle$
  oracle. Thus, \advB can output at least $n+1$ valid signatures, which
  contradicts security of \SBCM.
  %
  By assumption of security of \SBCM, $\Pr[W_3]$ must therefore be negligible in
  $\SBCMsecpar$ and, consequently: $\AdvGSACTrace(\secpar) = \negl(\SBCMsecpar)+
  \negl(\NIZKsecpar)$, which is negligible.  
  \qed
\end{proof}

\begin{proof}[\thmref{thm:frame-gsac}; Non-frameability of \GSACGen]
  Consider the following events:

  \begin{description}
  \item[$U \coloneqq \uid \in \HU$.] The user identifier associated to the
    signature does not belong to an honest user.
  \item[$S \coloneqq \sig \notin \SIG\lbrack \uid \rbrack$.] The signature was
    not produced via a call to the \SIGN oracle.
  \item[$A \coloneqq \dattrs \not\subseteq \attrs$.] The revealed attributes are
    note a subset of the attributes output by $\adv$ and accepted by \Judge.
  \end{description}

  $\adv$ wins if:

  \begin{enumerate}
  \item $U \land S$. The adversary outputs a signature framing an honest user
    who did not produce it.
  \item $U \land A$. The adversary outputs a signature framing an honest user,
    since the revealed attributes are not a subset of the attributes accepted
    by \Judge.
  \end{enumerate}

  The probability of $\adv$ winning due to $U \land A$ is negligible, after
  soundness of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.

  Concerning $U \land S$, we build an adversary \advB who, given an adversary
  $\adv$ against \ExpGSACNonframe via this condition, breaks the hiding property
  of \C.

@@

  We now build \advB from $G_1$. Recall that \advB is an adversary against
  hiding of \C and, thus, receives a commitment \Ccom, committing to one out
  of two possible messages, $\msg_0$ and $\msg_1$, which \advB picks at random
  from $\AttrSpace$. \advB initializes everything as $G_1$ and, in addition,
  chooses a random integer $u \in [q]$, where $q$ will be the maximim number of
  users to let $\adv$ create via calls to the \HUGEN oracle (note though that
  $q$ can be as large as desired, as long as it remains a polynomial function of
  the security parameter). In the $u$-th call to the \HUGEN oracle, \advB
  ignores $(\upk,\usk)$ to $(\Ccom,\bot)$. Calls to the \OBTAIN and \SIGN oracles
  are dealt with as usual, except when $\adv$ requests credentials or signatures
  on behalf of the $u$-th user. In that cases, \advB simulates the corresponding
  NIZK proofs by calling $\NIZKSim^{\NIZKRel_{\Issue}}$ or
  $\NIZKSim^{\NIZKRel_{\Sign}}$, respectively. Due to the
  simulation-extractability property of both NIZK systems, the output produced
  by the oracles is indistinguishable from that in $G_1$ and, consequently, from
  $G_0=\ExpGSACNonframe$.

  Finally, assume that $\adv$ wins \ExpGSACNonframe with non-negligible
  probability. This means that it outputs a $(\sig = (\Ec,\sEc^{\attrs},
  \pi_\sig),\dattrs,\msg,\upk,\attrs,\oproof)$, where $(\sig,\dattrs,\msg)$ are
  accepted by \Verify, and $(\upk,\attrs,\oproof,\sig,\dattrs,\msg)$ are
  accepted by \Judge. Thus, after soundness
  of $\NIZK^{\NIZKRel_{\Sign}}$ and $\NIZK^{\NIZKRel_{\Open}}$, we know that
  \upk is the correct public key associated to an honest user \uid, but as per
  the winning condition, \sig has not been produced via a call to the \SIGN
  oracle for a \cid owned by \uid. Therefore, we can extract the \usk
  corresponding to \upk from the $\pi_{\sig}$ proof. Since executions in the
  environment prepared by \advB are indistinguishable to $\adv$ from executions
  of $G_0$, we can assume that the probability that the \uid associated to the
  \sig output by $\adv$ equals $1/q$. In that case, \usk precisely matches
  $\msg_b$, and \advB wins the hiding game against \C. Since we assume \C
  to be hiding, this probability must therefore be negligible.   
  \qed
\end{proof}

### 2022-05-10 prism-backend/research/gsac/security-gsac.tex
Updated GSAC and UAS proofs based on updated non-frame definiton.

\begin{theorem}[Non-frameability of \GSACGen]
  \label{thm:frame-gsac}
  If the underlying scheme for $\NIZK^{\NIZKRel_{\Issue}}$,
  $\NIZK^{\NIZKRel_{\Sign}}$ and $\NIZK^{\NIZKRel_{\Open}}$ are sound,
  zero-knowledge, and simulation-extractable, and
  the commitment scheme \C is hiding, then our generic \GSACGen construction
  satisfies non-frameability as defined in \defref{def:frame-gsac}, except with
  negligible probability.
\end{theorem}

>>>>

\begin{theorem}[Non-frameability of \GSACGen]
  \label{thm:frame-gsac}
  If the scheme for $\NIZK^{\Issue}$ is zero-knowledge, the scheme for
  $\NIZK^{\Sign}$ is zero-knowledge and sound, the scheme for $\NIZK^{\Open}$ is
  sound, and the commitment scheme \C is hiding, then our generic \GSACGen
  construction satisfies non-frameability as defined in \defref{def:frame-gsac},
  except with negligible probability.
\end{theorem}

### 2022-05-10 prism-backend/research/gsac/security-uas.tex
Updated GSAC and UAS proofs based on updated non-frame definiton.

\begin{proof}[\thmref{thm:correctness-uas}]
  \todo{XXX}
\end{proof}

@@

\begin{proof}[\thmref{thm:anonymity-uas}]
  In this proof, we restrict to the case in which the adversary can only make
  one query to the challenge oracle. Note however that the generalization to
  polynomially many queries given in \cite{bsz05} applies here too (with the
  corresponding security loss). Thus, proving security for one query to the
  challenge oracle is enough.

@@

\begin{proof}[\thmref{thm:issue-forge-uas}]
  We show that the probability that \fissue outputs $0$ is negligible, as well
  as the probability that the extracted \usk is not the one that was used to
  request some of the credentials employed to obtain the credential specified by
  the adversary.
  %
  For this purpose, we define two games, $G_0=\ExpForgeIssue$, and $G_1$, which
  is exactly the same, but where, within the \Setup algorithm, we replace
  $\NIZKSetup^{\Issue}$ with $\NIZKSimSetup^{\Issue}$. As per the definition of
  \NIZK in \appref{sapp:nizk}, both games are indistinguishable.

@@

\begin{proof}[\thmref{thm:sign-forge-uas}]
  As for \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
  and $G_1$, which is exactly the same but where, within the \Setup algorithm,
  we replace $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. After
  zero-knowledgeness of $\NIZK^{\Sign}$, both games are indistinguishable.

@@

\begin{theorem}[Non-frameability of \CUASGen]
  \label{thm:frame-uas}
  If the underlying NIZK schemes are zero-knowledge and the scheme used for
  $\NIZK^{\Sign}$ is simulation-extractable, and the commitment scheme is
  hiding, then our \CUASGen construction satisfies non-frameability as defined
  in \defref{def:frame-uas}, except with negligible probability.
\end{theorem}

\begin{proof}[\thmref{thm:frame-uas}]
  We prove that, given an adversary $\adv$ against non-frameability of \CUASGen,
  we can build an adversary \advB that breaks the hiding property of the
  underlying commitment scheme, with non-negligible probability.

>>>>

\begin{proof}[\thmref{thm:correctness-uas}; Correctness of \CUASGen]
  \todo{XXX}
\end{proof}

@@

\begin{proof}[\thmref{thm:anonymity-uas}; Anonymity of \CUASGen]
  In this proof, we restrict to the case in which the adversary can only make
  one query to the challenge oracle. Note however that the generalization to
  polynomially many queries given in \cite{bsz05} applies here too (with the
  corresponding security loss). Thus, proving security for one query to the
  challenge oracle is enough.

@@

\begin{proof}[\thmref{thm:issue-forge-uas}; Issue unforgeability of \CUASGen]
  We show that the probability that \fissue outputs $0$ is negligible, as well
  as the probability that the extracted \usk is not the one that was used to
  request some of the credentials employed to obtain the credential specified by
  the adversary.
  %
  For this purpose, we define two games, $G_0=\ExpForgeIssue$, and $G_1$, which
  is exactly the same, but where, within the \Setup algorithm, we replace
  $\NIZKSetup^{\Issue}$ with $\NIZKSimSetup^{\Issue}$. As per the definition of
  \NIZK in \appref{sapp:nizk}, both games are indistinguishable.

@@

\begin{proof}[\thmref{thm:sign-forge-uas}; Sign unforgeability of \CUASGen]
  As for \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
  and $G_1$, which is exactly the same but where, within the \Setup algorithm,
  we replace $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. After
  zero-knowledgeness of $\NIZK^{\Sign}$, both games are indistinguishable.

@@

\begin{theorem}[Non-frameability of \CUASGen]
  \label{thm:frame-uas}
  If the underlying scheme for $\NIZK^{\Issue}$ is zero-knowledge, the scheme
  for $\NIZK^{\Sign}$ is zero-knowledge, sound and simulation-extractable, the
  scheme for $\NIZK^{\Open}$ is zero-knowledge and sound, and the commitment
  scheme is hiding, then our \CUASGen construction satisfies non-frameability as
  defined in \defref{def:frame-uas}, except with negligible probability.
\end{theorem}

\begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]
  First, note that the adversary wins if it produces a signature that traces to
  an honest user (which, in our case, is tested by checking whether the
  extracted \usk belongs ot an honest user); and, in addition, either (1) the
  signature was not produced via a call to the \SIGN oracle, or (2) the opening
  value output by the adversary and accepted by \Judge, does not match the
  extracted one (i.e., the one used as witness to $\NIZKRel^{\Sign}$). Note that
  the probability of (2) is negligible due to soundness of $\NIZK^{\Sign}$ and
  $\NIZK^{\Open}$, given that \Verify and \Judge accept the signature and
  opening proof.

  Next we prove that, given an adversary $\adv$ against non-frameability of
  \CUASGen, under condition (1) above, we can build an adversary \advB that
  breaks the hiding property of the underlying commitment scheme, with
  non-negligible probability.
